Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131$-$1231 at $z$=0.654

### 2016-07-07 WRITEUP/ms.tex
update MBH-Mbulge using updated MBH from Sluse07, updated intro, update velocity offset

\begin{abstract}
We present interferometric observations of \bco and \cco emission toward the ``Einstein ring''
RXS J1131$-$1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
RXJ1131 is gravitationally lensed quasar.
Spatially and spectrally resolved.This is the first resolved \bco imaging at intermediate redshift.
The molecular gas of $M_{\rm gas}$\eq123BLAH\E{10}\,\Msun in the host galaxy 
is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
RXS J1131-1231 a wet-merger, 
Dynamical lens modeling, the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
is indicative of, and suggests...
% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
The gas mass fraction of $\sim$19\%, consistent with the trend of decreasing gas fraction at this epoch.
% MBH-sigma relation...
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
Studies of galaxy evolution have been focusing on the interplay between baryonic physics
(\eg feedback and gas dissipation) and \SF and active galactic nucleus (AGN) activity across cosmic epochs.
It is not well-understood when and how baryons of present-day galaxies were assembled, 
but it is clear that both the co-moving \SF rate and black hole accretion rate densities
increased substantially since $z$\,$>$\,3 and reached their climax at $z$\ssim2, followed by 
a rapidly decline toward $z$\ssim0 \citep[\eg][]{Hopkins06a, Madau14a}. 
% Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
A leading explanation for this decline is related to the evolution of molecular gas content and 
\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
but confirmation from direct molecular gas measurements at intermediate redshift 
$($0.2\,$<$\,$z$\,$<$\,1$)$ is still limited both in number and in the variety of galaxy populations probed --- 
only unresolved CO observations have been carried out for $\sim$\,70 ULIRGs up to date \citep{Combes11a, Combes13a}.

In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
grows by accretion of the cold molecular gas from its host galaxy.
Meanwhile, empirical scaling relations such as the Magorrian relation \citep{Magorrian98a}
--- a tight correlation between black hole mass and stellar bulge mass ---
have been established locally, implying a self-regulating co-eval growth between local SMBHs and their host galaxies.
Attempts to extend this relation out to higher redshifts, beyond the peak epoch 
of \SF and AGN activity, have been made in recent years.
It has been reported that the $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of high-$z$ submillimeter galaxies (SMGs) falls below 
the local relation \citep[\eg][]{Borys05a,Alexander08a} but that of high-$z$ quasar host galaxies are found 
lying above 
the relation \citep[\eg][]{McLure06a,Peng06a}.
Stellar mass of quasar host galaxies at $z$\,$>$\,4 constrained by their CO-based dynamical mass 
are also too small compared to that based from the local relation \citep{Walter04a, Riechers08a,Coppin08a}. 
It is evident that high-$z$ galaxies deviates from the local relation, and among their galaxy populations, but
the AGN-host galaxy connection at intermediate redshift is still poorly-constrained. 
This owes to the difficulties in measuring stellar emission in the host galaxy under the presence of a bright quasar, or alternatively
owing to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass. 
With gravitational lensing, emission of the background quasar and its host galaxy 
is magnified and stretched out to different extents, and is projected to different locations in the image plane.
This in effect increases the surface brightness contrast between their emission and allows for the
relatively uncontaminated measurements of their emission.

\defcitealias{Sluse03a}{S03}
The ``Einstein ring'' RXS J113151.62$-$123158 (hereafter RXJ1131) 
at $z_\textrm{s, QSO}$\eq0.685 \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the 
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration and its redshift.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of radius 1\farcs83
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
We have thus carried out a detailed study for RXJ1131, as presented in this paper.
RXJ1131 is strongly lensed by an elliptical galaxy at $z_\textrm{L}$\eq0.295 \citepalias{Sluse03a}.
The black hole residing in RXJ1131 is rotating with a high spin parameter
\citep[$a$\,$\sim$\,0.9;][]{Reis14a}. 
Previous studies also report a black hole mass of
\mbh\,$<$\,2\E{8}\Msun\footnote{Various values for the black hole 
mass have been reported based on the different methods and normalizations used. \citet{Dai10a} find a 
\mbh\ssim10$^{8}$\,\Msun using the virial estimator with H$\beta$ linewidth,
and \citet{Pooley07a} report $M_{\rm BH}$\,=\,2.5\E{7}\,\Msun using the
AGN bolometric luminosity of $L_{\rm bol, X}$ =1.3\E{45}\, ergs\,s\pmOne, 
assuming $L$$/$$L_\textrm{Edd}$ = 0.25 and $\eta$ = 0.15.}.

@@

Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF).
In each model, we require a target acceptance rate of $\sim$0.25$-$0.5
and check for chain convergence by inspecting trace plots
and requiring the samples are beyond at least an autocorrelation time.
We thus employ $\sim$50,000 samples as the initial ``burn-in'' phase
to stabilize the Markov chains (which we then discard) and
use the final $\sim$5,000 steps, sampled by 128 walkers, to identify
the posterior. Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.
\input{table_medianLens}

@@

We then attempt to characterize the molecular gas kinematics using an
empirically-motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{a} \arctan(\frac{R}{R_{t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center,
$V_{a}$ is the asymptotic velocity, and $R_{t}$ is the ``turnover''
radius at which the rotation curve becomes flat.
We perform non-linear least square fitting using an orthogonal distance
regression to find the best-fit parameters,
taking into account the uncertainties in both velocity (channel width) and
distance offset. We also place an upper limit on $R_{t}$\,$<$15 kpc
to keep this parameter physical \citep[\eg][]{Puech08a,Miller11a}.
The parameter uncertainties are inferred based on a Monte Carlo simulation
of 500 iterations, where the input parameters are perturbed
according to random Gaussian distributions of sigmas
corresponding to their uncertainties.
Using this model, we find $V_{a}$\,=\,975\,$\pm$\,387 \kms,
$R_{t}$\,=\,10.7\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
However, since emission is not resolved along the flat regime
of the rotation curve, the asymptotic velocity is poorly constrained and
the ``turnover'' radius is at most an upper limit.
In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.

@@

The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is not equivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disk rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disk scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disk peaks \citep{Courteau97b}.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
lens model (\citetalias{Claeskens06a}; converted to
our cosmology).
We note that the source plane half-light radius varies substantially with
wavelength. In particular, the half-light radius is found to be
$\sim$\,4\,kpc and $\sim$7\,kpc in $V$-band
\citepalias{Brewer08a} and $H$-band \citepalias{Claeskens06a}, respectively.
The CO gas is thus of similar spatial
extent as in $H$ and $I$-bands.

In the rest-frame,
emission in the observed-frame $H$-band corresponds to NIR emission $(\sim$1\,$\micron)$,
tracing radiation from the accretion disk surrounding
the central AGN and also from old and evolved stellar populations;
$I$-band corresponds to roughly the optical $V$-band, tracing stellar radiation from
existing, less massive (\ie longer-lasting) stars;
$V$-band corresponds to roughly $U$-band,  tracing radiation from massive young stars
in the host galaxy. Hence,
the $V$-band compactness may be explained in part
due to the fact that its emission is
more susceptible to dust extinction than in other bands and/or
a central starburst caused by higher
concentrations of star-forming gas towards the central regions -- owing to
gravitational perturbations induced
from interactions with the companion
\citep[\eg][]{DiMatteo05a}.
This is consistent with the picture that old stars form first and constitute the bulge component
of a spiral galaxy and that nuclear starbursts (in the inner few kpc) can be triggered 
in a later time as the progenitor disk galaxy interacts with other galaxies, 
and thereby forming a larger bulge.

@@

\subsection{Velocity Offset and a Recoiling Black Hole}
Using the CO line center redshift as the systemic redshift, we find
a velocity offset of $\sim$780\,\kms from the optical
\mgii line and the \oiii lines \citepalias[$z_{\rm QSO} = 0.658$;][]{Sluse03a}. This implies that the AGN is dynamically offset from the centroid of its host galaxy. 
From the CO channel maps in \Fig{CO21mom} and \Fig{chanmap}, it is also apparent that the 
line center of the gas is not co-spatial with the optical quasar as the point-like images
along the lensing arc
are spatially offset to the NW of the CO line center.
While spatial offsets between optical lines and CO line
have been reported in other galaxies, the velocity offsets are typically $\lesssim$\,500\kms.
{\bf
In the classical SDSS analysis for line offsets \citep{Richards02a}?.
\oiii and \mgii analysis \citep{Boroson05a, Bae14a}?.
with the corresponding trends and possible explanations?.
More extreme offsets between CO and optical lines have been seen \citep{Hainline04a} 
or between \cii and \mgii \citep[\eg][]{Venemans16a}.}
For instance, the
velocity offset in
an SDSS sample of ongoing mergers at $z$\,$<$\,0.21 is at most $\sim$410\,km/s \citep{Comerford14a}.

A large velocity offset can also result from a recoiling black hole (BH) where its broad line region
is moving at high velocity relative to the bulk of its host galaxy 
\citep{Madau04a, Bonning07a, Loeb07a}. 
Such a scenario is expected to occur 
when a pair of uneven mass BH coalesce, during which their orbital energy is being released 
as gravitational wave and a 
non-zero net angular momentum is being carried away.
Depending on their initial conditions, numerical relativity simulations have shown that
the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
%While such large velocity offsets are theoretically achievable,
%they are not commonly observed --- only a few objects 
%have been reported with optical offsets $\gtrsim$1000\,\kms. For instance,
%the most promising candidate with both spectroscopy and imaging
%signatures of a recoiling BH is CID-42 at $z$\,=\,0.359, with 
%an offset of $\sim$1300\,\kms between the narrow and broad component of H$\beta$ \citep{Civano10a}.
%Other example includes the type-1 QSO SDSS 0956+5127 at $z$\,$\sim$\,0.714, with an offset of 1200\,\kms
%between Mg{\scriptsize II}~2798\AA\ and $[$O{\scriptsize III}$]$~4959, 5007\AA\ lines
%\citep{Steinhardt12a}. % but here its between CO and optical lines
%% SDSSJ0927+2943 at $z$\,$\sim$\,0.713, with an offset of 2650\,\kms \citep{Komossa08a}, but disproved by Decarli+14; Hence, I am going to cut this out because I listed this source here just to demonstrate the scarcity of high velocity offsets; but the offset in this system is between a set of redshifted versus a set of blueshifted.. which is not quite the same our case here.
The fact that the BH in RXJ1131 has a high spin parameter \citep{Reis14a}
renders this scenario a viable option for the origin
of the velocity offset. 
However, since this model requires a merged BH, this interpretation would imply RXJ1131 have 
already encountered with the companion galaxy, which is consistent with
the highly spinning BH observed in RX1131.
Given the presence of a nearby companion observed in our data, the system may be in its 
subsequent stages of (minor) merging resulting from previous passage of a major merger.

As demonstrated here using \mgii and \oiii lines, large velocity offsets between CO and optical lines may be present.
We thus caution against the use of optical lines as 
true systematic redshift indicators as the resulting redshift can deviate from the 
true value.

\subsection{The $M_{\rm BH}$$-$\mdyn Relation}
% the gas mass of RXJ1131 is 1.3\E{10}\,\Msun, 
% dynamical mass in RXJ1131 is $\sim$8.3\E{10}\,\Msun 
% total dust mass in the merging system is $\sim$2-4\E{8}\,\Msun,  % using CO magnification factor
Assuming RXJ1131 follows the local $M_{\rm BH}$$-$$M_{\rm bulge}$ relation reported by \citet{HR04a}, 
the virial-based black hole mass \mbh$\sim$\,6\E{7}\,\Msun \citep{Peng06a} corresponds 
to a stellar bulge mass of $M_{\rm bulge}$\eq4.2\E{10}\,\Msun.
This implies that the bulge component is responsible for making up roughly half the dynamical mass. 
If we subtract the black hole mass, gas mass, and dust mass\footnote{Here, we adopt the lowest dust mass among the two SED models to derive an upper limit on the stellar mass.}
from the dynamical mass and ignore a contribution from the dark matter, this would
yield an upper limit on the stellar mass of 6.8\E{10}\,\Msun. 
Thus, the bulge mass derived above based on the local relation is not physically infeasible.
The stellar mass upper limit would also imply a lower limit on the 
$M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $\sim$0.09\%, which falls below the local relation 
but is consistent within the range found in other intermediate-$z$ radio-loud AGNs \citep{McLure06a}. 
A dark matter fraction of over $f_{\rm DM}$\ssim0.6 would be needed for RXJ1131 to 
lie above the local relation and fall outside the range of $M_{\rm BH}$$/$$M_{\rm bulge}$ found in 
\citep{McLure06a}. 
% local: $M_{\rm BH}$/$M_{\rm bulge}$\ssim0.14\% or equivalently $\log{M_{\rm BH}/M_{\rm bulge}}$\ssim$-$2.85,

\subsection{Dynamical lens modeling of high-$z$ quasars}
%
Riechers08a is the only other similar system at emission in host galaxy lensed into an Einstein ring configuration and
with dynamical lens modeling of CO.
Which also velocity gradient.
Constraints on the.

\subsection{Others}
Comparing the spatial extents of the CO with the stellar components traced by {\it HST}\\
The dusty nature of this system?? \\
compare to Riechers08a \\=
{\bf compare to J04135 in R13} \\

@@

We observe \bco and \cco line emisison toward the
quadruply-lensed quasar RXJ1131 at $z_{\rm CO}$\,$\sim$0.65 
using the PdBI and CARMA, benchmarking the 
first resolved interferometric CO imaging at intermediate redshift.
The brightness temperature ratio between \bco and \cco of $r_{32}$ = BLAH, which taking into 
account the large phase errors associated with \cco, is consistent with
thermalized excitation between these lines in other ULIRGs.
The (gas) mass ratio, the intrinsic CO line profile,
and the source-plane velocity field are all evident of
a minor merger, in good agreement with previous studies of RXJ1131 in the optical \citepalias{Claeskens06a,Brewer08a}.

>>>>

\begin{abstract}
We present interferometric observations of \bco and \cco emission toward the ``Einstein ring''
RXS J1131$-$1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
RXJ1131 is gravitationally lensed quasar.
Spatially and spectrally resolved.This is the first resolved \bco imaging at intermediate redshift.
The molecular gas of $M_{\rm gas}$\eq123BLAH\E{10}\,\Msun in the host galaxy 
is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
RXS J1131-1231 a wet-merger, 
Dynamical lens modeling, the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
turbulent disk
is indicative of, and suggests...
% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
The gas mass fraction of $\sim$19\%, consistent with the trend of decreasing gas fraction at this epoch.
% MBH-sigma relation...
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
Studies of galaxy evolution have been focusing on the interplay between baryonic physics/process
(\eg feedback and gas dissipation) and \SF and active galactic nucleus (AGN) activity across cosmic epochs.
It is not well-understood when and how baryons of present-day galaxies were assembled, 
but it is clear that both the co-moving \SF rate and black hole accretion rate densities
increased substantially since $z$\,$>$\,3 and reached their climax at $z$\ssim2, followed by 
a rapidly decline toward $z$\ssim0 \citep[\eg][]{Hopkins06a, Madau14a}. 
% Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
A leading explanation for this decline is related to the evolution of molecular gas content and 
\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
but confirmation from direct molecular gas measurements at intermediate redshift 
$($0.2\,$<$\,$z$\,$<$\,1$)$ is still limited both in number and in the variety of galaxy populations probed --- 
only unresolved CO observations have been carried out for $\sim$\,70 ULIRGs up to date \citep{Combes11a, Combes13a}.

% In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
% grows by accretion of the cold molecular gas from its host galaxy.
Meanwhile, empirical scaling relations such as the Magorrian relation \citep{Magorrian98a}
--- a tight correlation between black hole mass and stellar bulge mass ---
have been established locally, implying a self-regulating co-eval growth between local SMBHs and their host galaxies.
Attempts to extend this relation out to higher redshifts, beyond the peak epoch 
of \SF and AGN activity, have been made in recent years.
It has been reported that the $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of high-$z$ submillimeter galaxies (SMGs) falls below 
the local relation \citep[\eg][]{Borys05a,Alexander08a} but that of high-$z$ quasar host galaxies are found 
lying above 
the relation \citep[\eg][]{McLure06a,Peng06a}.
Stellar mass of quasar host galaxies at $z$\,$>$\,4 constrained by their CO-based dynamical mass 
are also too small compared to that based from the local relation \citep{Walter04a, Riechers08a,Coppin08a}. 
While it has become clearer that high-$z$ galaxies deviates from the local relation, and among their galaxy populations, 
such a picture is still unclear  at intermediate redshift.
This owes to the difficulties in measuring stellar emission in the host galaxy under the presence of a bright quasar, or alternatively
owing to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass. 
With gravitational lensing, emission of the background quasar and its host galaxy 
is magnified and stretched out to different extents, and is projected onto different locations in the image plane.
This in effect increases the surface brightness contrast between their emission and allows for the
relatively uncontaminated measurements of their emission.

\defcitealias{Sluse03a}{S03}
The ``Einstein ring'' RXS J113151.62$-$123158 (hereafter RXJ1131) 
at $z_\textrm{s, QSO}$\eq0.685 \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the 
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of radius 1\farcs83
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
We have thus carried out a detailed study for RXJ1131 as presented in this paper.
RXJ1131 is strongly lensed by an elliptical galaxy at $z_\textrm{L}$\eq0.295 \citepalias{Sluse03a}.
The moderate mass black hole $M_{\rm BH}$\eq8\E{7}\Msun \citep{Sluse12a} %based on H beta line
residing in RXJ1131 is rotating with a high spin parameter \citep[$a$\,$\sim$\,0.9;][]{Reis14a}, and
is radiating at an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq1.3\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.

@@

Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF).
In each model, we require a target acceptance rate of $\sim$0.25$-$0.5
and check for chain convergence by inspecting trace plots
and by requiring the samples are obtained beyond at least an autocorrelation time.
We thus employ $\sim$50,000 samples as the initial ``burn-in'' phase
to stabilize the Markov chains (which we then discard) and
use the final $\sim$5,000 steps, sampled by 128 walkers, to identify
the posterior. Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.
\input{table_medianLens}

@@

We then attempt to characterize the molecular gas kinematics using an
empirically-motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{a} \arctan(\frac{R}{R_{t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center,
$V_{a}$ is the asymptotic velocity, and $R_{t}$ is the ``turnover''
radius at which the rising part of the curve begins to flatten.
We perform non-linear least square fitting using an orthogonal distance
regression to find the best-fit parameters,
taking into account the uncertainties in both velocity (channel width) and
distance offset. We also place an upper limit on $R_{t}$\,$<$15 kpc
to keep this parameter physical \citep[\eg][]{Puech08a,Miller11a}.
The parameter uncertainties are inferred based on a Monte Carlo simulation
of 500 iterations, where the input parameters are perturbed
according to random Gaussian distributions of sigmas
corresponding to their uncertainties.
Using this model, we find $V_{a}$\,=\,975\,$\pm$\,387 \kms,
$R_{t}$\,=\,10.7\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
However, since emission is not resolved along the flat regime
of the rotation curve, the asymptotic velocity
and the ``turnover'' radius are poorly constrained.
In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.

@@

The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is not equivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disk rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disk scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disk peaks \citep{Courteau97b}. % \ie commonly use Vmax (taken at R2.2) as V_rot
Here, we adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6\,$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
lens model (\citetalias{Claeskens06a}; converted to
our cosmology).
We note that the source plane half-light radius varies substantially with
wavelength. In particular, the half-light radius is found to be
$\sim$\,4\,kpc and $\sim$7\,kpc in $V$-band
\citepalias{Brewer08a} and $H$-band \citepalias{Claeskens06a}, respectively.
The CO gas is thus of similar spatial
extent as in $H$ and $I$-bands.

In the rest-frame,
emission in the observed-frame $H$-band corresponds to NIR emission $(\sim$1\,$\micron)$,
tracing radiation from the accretion disk surrounding
the central AGN and also from old and evolved stellar populations;
$I$-band corresponds to roughly the optical $V$-band, tracing stellar radiation from
existing, less massive (\ie longer-lasting) stars;
$V$-band corresponds to roughly $U$-band,  tracing radiation from massive young stars
in the host galaxy. Hence,
the $V$-band compactness may be explained in part
due to the fact that its emission is
more susceptible to dust extinction than in other bands and/or
a central starburst caused by higher
concentrations of star-forming gas towards the central regions -- owing to
gravitational perturbations induced
from interactions with the companion
\citep[\eg][]{DiMatteo05a}.
This is consistent with the picture that old stars form first and constitute the bulge component
of a spiral galaxy and that nuclear starbursts (in the inner few kpc) can be triggered 
at a later time as the progenitor disk galaxy interacts with other galaxies to form a larger bulge.

@@

\subsection{Velocity Offset and a Recoiling Black Hole}
%Outflow:
% Not AGN outflows because require different velocity offsets in Balmer and forbidden lines (Zamanov02a)
% line origins:
% \mgii & Hbeta: outer part of the BLR (Goad12a) compared to high-ionization lines (\eg CIV)
% Hbeta can also come from NLR

\defcitealias{Sluse07a}{S07}
\citet[hereafter S07]{Sluse07a} report two sets of AGN lines observed in RXJ1131. 
The first set of lines is at $z$\ssim0.653, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and 
the \mgii emission line.
Using the CO line center redshift as the systemic redshift, the second set of lines is blueshifted by $\sim$780\,\kms.
This implies 
that the broad line region (BLR) of the AGN is dynamically offset from the centroid of its host galaxy.
We confirm this spatially in the channel maps in \Fig{CO21mom} and 
\Fig{chanmap}, where the line center of the CO gas is not co-spatial 
with the optical quasar --- the point-like images along the lensing arc is 
offset to the NW of the CO line center emission. 
On the other hand, we find that the redshift of the \oiii lines tracing the narrow line region (NLR) 
is fully consistent with the systemic redshift, supporting previous claims that \oiii lines are good proxies
to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
% since BLR are gravitationally bound to BH, and NLR may not be

%Velocity Offsets of $\lesssim$\,500\,\kms in other AGNs and their host galaxies have been reported in the literature.
%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s 
%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption

Large velocity offsets between emission lines of the
BLR and the NLR may arise in a recoiling black hole (BH),
% recoiling SMBHs as well as subparsec-scale binary SMBHs produce velocity offsets in the broad AGN emission lines and not the narrow AGN emission lines (e.g., Gaskell 1983; Bonning et al. 2007; Eracleous et al. 2012; Ju et al. 2013; Shen et al. 2013). 
where its BLR is moving at high velocity relative to the bulk of its host galaxy 
\citep{Madau04a, Bonning07a, Loeb07a}.
A recoiling black hole is expected 
when a pair of uneven mass BH coalesce, during which their orbital energy is being released 
as gravitational wave and a 
non-zero net angular momentum is being carried away.
Depending on their initial conditions, numerical relativity simulations have shown that
the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a} and
SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}.
%To date, the most promising candidate with both spectroscopy and imaging
%signatures of a recoiling BH is CID-42 at $z$\,=\,0.359, with 
%an offset of $\sim$1300\,\kms between the narrow and broad component of H$\beta$ \citep{Civano10a}.
%This is similar to the case here for RXJ1131, where the two components of H$\beta$ are offset by 
%\ssim550\,\kms.
%Other example of recoiling BH 
%includes the type-1 QSO SDSS 0956+5127 at $z$\,$\sim$\,0.714, with an offset of 1200\,\kms 
%between \mgii and \oiii lines \citep{Steinhardt12a}.
One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, \citet{Komossa08a} 
suggest the possibility of a recoiling black hole in this system due to an offset of 2650\,\kms 
between a set of narrow emission lines and a second set of broad Balmer 
and high-ionization forbidden lines.  % offset in this system: between a set of redshifted (narrow) versus a set of blueshifted (broad).
However, this scenario is refuted recently by \citet{Decarli14a}, who confirm that the
BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.
This is in contrast with the case in RXJ1131, our CO observations confirm the blueshifted BLR lines.
The fact that the BH in RXJ1131 has a high spin parameter \citep{Reis14a}
renders the recoiling BH scenario a viable option for the origin of the blueshift. 
Since this model requires a merged BH, this interpretation would imply RXJ1131 have 
already encountered with the companion galaxy, which could explain
the highly spinning BH observed in RX1131.
In this picture, the presence of a nearby companion observed in our data may reflect that RXJ1131 is in its 
subsequent stages of (minor) merging resulting from previous passage of a major merger.

\subsection{The $M_{\rm BH}$$-$\mdyn Relation}
% the gas mass of RXJ1131 is 1.3\E{10}\,\Msun, 
% dynamical mass in RXJ1131 is $\sim$8.3\E{10}\,\Msun 
% total dust mass in the merging system is $\sim$2-4\E{8}\,\Msun,  % using CO magnification factor
Assuming RXJ1131 follows the local $M_{\rm BH}$$-$$M_{\rm bulge}$ relation reported by \citet{HR04a}, 
the virial-based black hole mass \mbh$\sim$\,8\E{7}\,\Msun \citep{Sluse12a} corresponds 
to a stellar bulge mass of $M_{\rm bulge}$\eq5.4\E{10}\,\Msun.
% \ie $M_{\rm BH}$/$M_{\rm bulge}$\ssim0.15\% or equivalently $\log{M_{\rm BH}/M_{\rm bulge}}$\ssim$-$2.83
This implies that the bulge component is responsible for making up $\sim$65\% of the dynamical mass. 
If we subtract the black hole mass, gas mass, and dust mass\footnote{Here, we adopt the lowest dust mass among the two SED models to derive an upper limit on the stellar mass. Since the dust mass only contributes a small fraction of the total mass, a factor of $\sim$2 difference is minor.}
from the dynamical mass and ignore a contribution from the dark matter, this would
yield an upper limit on the stellar mass of 6.8\E{10}\,\Msun. 
Thus, the bulge mass derived above based on the local relation is not unphysical.
The stellar mass upper limit would also imply a lower limit on the 
$M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $\sim$0.12\%, which is consistent with the local relation within the scatter and with other intermediate-$z$ radio-loud AGNs \citep{McLure06a}. 
%Depending on the exact dark matter fraction, RXJ1131 may lie above the local $M_{\rm BH}$/$M_{\rm bulge}$.

A dark matter fraction of over $f_{\rm DM}$\ssim0.5 within the radius of which we used to derive the 
dynamical mass (\ie $\lesssim$\,6\,kpc or $\sim$\,0.6$R_e$) would be required for RXJ1131 to 
lie above the local relation and fall outside the range of $M_{\rm BH}$$/$$M_{\rm bulge}$ found in 
\citet{McLure06a}, which is unlikely given its dynamical mass and rotation velocity 
% \ie based on the dark matter fraction as a function of half light radius found; Figure 2 in Courteau15
% Courteau15a: f<0.5 at 0.6*Re for gal. with cir. velocity like RXJ1131
\citep{Courteau15a}.
% $f_\textrm{DM}$ is expected to increase with cosmic time \citep{Beifiori14a} and that the local DM fraction is 16-28% from dynamical studies \citep{Thomas11a, Cappellari13a} and based on predictions from simulations of 18%-38% \citep{Naab07a}.

@@

We observe \bco and \cco line emisison toward the
quadruply-lensed quasar RXJ1131 at $z_{\rm CO}$\,$\sim$0.65 
using the PdBI and CARMA, benchmarking the 
first resolved interferometric CO imaging at intermediate redshift.
The brightness temperature ratio between \bco and \cco of $r_{32}$ = BLAH, which taking into 
account the large phase errors associated with \cco, is consistent with
thermalized excitation between these lines in other ULIRGs.
The (gas) mass ratio, the intrinsic CO line profile,
and the source-plane velocity field are all evident of
a minor merger, in good agreement with previous studies of RXJ1131 in the optical \citepalias{Claeskens06a,Brewer08a}. 
{\bf Say more about dusty nature, IR luminous, gas-rich, CO and stellar emission.}
We were able to compare the CO size with the stellar size because of lensing, and the uniqueness of this source. 
From dynamical constraints on the companion and the fact that RXJ1131 is optically bright, implies 
a large portion of the dust from SED fitting is residing in the companion and not RXJ1131. %so probably also means dust magnification factor is quite different, probably higher, because the companion CO magnification is also higher than the median CO, implying its in a lensing configuration with higher magnification.
